---
title: "Refword ASD analyses"
author: "Mike Frank & Dan Yurovsky"
date: "Sept 16, 2015"
output: html_document
---

```{r}
library(tidyverse)
library(purrr)

# #load libraries for data manipulation and graphing
library(xtable)
library(data.table)
library(jpeg)
library(XML)
library(magrittr)
library(zoo)
library(langcog)

```

# Constants

```{r}
#try/catch for different number of calib points
MAX_HEADER_ROWS <- 40

video = 1

VIDEOS = c("reflook", "birthday", "kitchen") #, "soc_word")

LEARN_STIMS = list("reflook4_4.avi", "ref-asd-birthday2.avi", 
                "ref-asd-kitchen2.avi") #, SOCWORD_LEARN_STIMS)

CALIB_STIMS = c("reflook4_4.avi", "ref-asd-birthday2.avi",
                "ref-asd-kitchen2.avi","calib.avi")
CALIB_STIM_LENGTHS <- c(NA,NA,NA,11.344)
CALIB_STIM_LENGTH <- CALIB_STIM_LENGTHS[video]


EXCLUDED_STIMS <- read.csv(paste0("metadata/loading_files/",
                                  VIDEOS[video],"_excluded.csv"),header = FALSE)$V1

LEARN_STIM <- LEARN_STIMS[video]
CALIB_STIM <- CALIB_STIMS[video]

X_MAX <- 1680
Y_MAX <- 1050

CALIB_SACCADE_time <- .3

FRAME_RATE <- 30

IMG_WIDTHS = c(1280,1920,1920,720) #960
IMG_HEIGHTS = c(720,1080,1080,720) #540

IMG_WIDTH = IMG_WIDTHS[video]
IMG_HEIGHT= IMG_HEIGHTS[video]

SCALE_X = X_MAX/IMG_WIDTH
SCALE_Y = Y_MAX/IMG_HEIGHT

LEARN_STIM_LENGTHS = c(256.823, 293.493, 307.373, NA)

LEARN_STIM_LENGTH <- LEARN_STIM_LENGTHS[video]

TEST_LENGTHS <- c(6, 6, 6, 7.5)
TEST_LENGTH <- TEST_LENGTHS[video]

AOI_BUFFER <- 25

GROUP <- "child"
ET_DATA_DIR <- "raw_data/"
# ET_DATA_DIR <- "ground_truth_test/"
# ET_DATA_DIR <- "raw_data_pilots/"
```

# Read all raw data 

```{r}
source('loading_helpers/et_helper.R')
files <- list.files(path = ET_DATA_DIR, pattern = '*.txt',
                    all.files = FALSE)

info <- map_df(paste0(ET_DATA_DIR, files), get_smi_header)

raw_data <- info %>%
  mutate(n = 1:n()) %>%
  split(.$n) %>%
  map_df(read_smi_idf)
```

Here's an observation. The tracker says the screen is 1680x1050 across all files. Yet the 
max x position in the raw data is 1280. 

Original image files are 1209 x 756
```{r}
hist(raw_data$lx)
hist(raw_data$ly)

max(raw_data$rx)
max(raw_data$ry)
```

Let's try looking at this by subject.
```{r}
p <- ggplot(raw_data, aes(x = lx, y = ly)) + 
  geom_point(alpha = .05) + 
  facet_wrap(~file_name)

p
```



```{r}
length(files)

tibble(name = str_replace(files,"PRPT_","") %>%
  str_replace("-eye_data Samples.txt","")) %>%
  separate(name, into = c("id","wks"), sep = "_") %>%
  pull(id) %>% unique() %>% length()
```


Undo stimulus hashing.

```{r}
hashes <- read_csv("stimuli_hashes/uniquehashes.csv") %>%
  rename(true_stimulus = X1, 
         hash = X2) %>%
  mutate(hash = str_replace(hash,"\">\n",""))

hashed_data <- raw_data %>%
  mutate(original_label = stimulus) %>%
  rename(hash = stimulus) %>%
  mutate(has_hash = str_length(original_label) > 30) %>%
  left_join(hashes) %>%
  mutate(true_stimulus = ifelse(has_hash, true_stimulus, original_label),
         true_stimulus = str_to_lower(true_stimulus))
```


The hash table was provided by Jared Gong to undo the terribleness of SMI stimuli getting mapped to different hashes for different subjects. Unfortunately, we don't have the stimulus log for several files. 

```{r}
filtered_data <- hashed_data %>%
  rename(stimulus = true_stimulus) %>%
  select(-hash, -has_hash, -original_label) %>%
  filter(str_detect(stimulus, "avi|jpg"), 
         str_length(stimulus) < 30, 
         !is.na(stimulus), 
         !str_detect(stimulus, "simpkids"))
```

Preprocess: average eyes, flip coords, etc.

```{r}
all_results <- preprocess_data(filtered_data) %>%
  mutate(subid = str_replace(str_replace(file_name, "raw_data/PRPT_", ""), 
                             "-eye_data Samples.txt","")) %>%
  mutate(x = ifelse(x == 0 | x >= width | y == 0 | y >= height, NA, x),
         y = ifelse(x == 0 | x >= width | y == 0 | y >= height, NA, y)) %>%
  mutate(x = ifelse(is.na(x), NA, x), 
         y = ifelse(is.na(y), NA, y)) %>% # get rid of NaN
  select(t, stimulus, subid, x, y) 
```

Let's just look at the xs and ys. 

```{r}
hist(all_results$x)
hist(all_results$y)
```


```{r}
hist(all_results$x[all_results$stimulus == "ref-asd-birthday2.avi"])
hist(all_results$y[all_results$stimulus == "ref-asd-birthday2.avi"])
```

```{r}
hist(all_results$x[all_results$stimulus == "r_bird_shoe.jpg"])
hist(all_results$y[all_results$stimulus == "r_bird_shoe.jpg"])
```

Sanity check. 

```{r}
filter(all_results, stimulus == "ref-asd-birthday2.avi") %>%
  ggplot(aes(x = x, y = y)) + 
  geom_point(alpha = .01) + 
  xlim(0,1680) + 
  ylim(0,1050)
```

```{r}
filter(all_results, stimulus == "ref-asd-birthday2.avi") %>%
  ggplot(aes(x = x, y = y)) + 
  geom_point(alpha = .01) + 
  xlim(0,1680) + 
  ylim(0,1050)
```

Something is horrible about the `t` values coming out of these files. 

Let's start by adjusting them so they all start within zero. Let's also make sure they are all measured in milliseconds.

```{r}
all_results %<>% 
  group_by(subid) %>% 
  mutate(t = (t - min(t))*1000) 

hist(all_results$t) 
```

There was some extra blank screen stuff shown to some kids at the end:

```{r}
qplot(filter(all_results, subid == "4013_24wk")$t, fill = filter(all_results, subid == "4013_24wk")$stimulus)
```

We can go back and do calibration adjustment if we want.

<!-- Calibration adjustment -->

```{r}
# source('loading_helpers/adjust_calibs.R')
# adjusted_data <- adjust_calibs(plot = FALSE, video = VIDEOS[video])
# adjusted_data <- all_results
```

```{r}
conditions <- all_results %>%
  filter(stimulus %in% LEARN_STIMS) %>%
  group_by(subid) %>%
  summarise(condition = stimulus[1]) %>%
  mutate(condition = case_when(condition == "reflook4_4.avi" ~ "reflook",
                               condition == "ref-asd-birthday2.avi" ~ "birthday",
                               condition == "ref-asd-kitchen2.avi" ~ "kitchen"))

all_results <- left_join(all_results, conditions)
```


# Test stimuli


Read in annotations.

```{r}
test_annotations <- lapply(VIDEOS, function (x) {
  read_csv(paste0("metadata/aois/", x, "_tests.csv")) %>%
    mutate(condition = x)
  }) %>%
  map_df(bind_rows) %>%
  mutate(stimulus = tolower(Stimulus),
         onset = onset * 1000) %>%
  select(-Stimulus) 
```

Now merge these in with the results.

```{r}
test_data <- all_results %>%
  filter(str_detect(stimulus, ".jpg" )) %>%
  filter(!(stimulus %in% EXCLUDED_STIMS)) %>%
  group_by(subid, stimulus) %>%
  mutate(t = t - min(t), 
         instance = ifelse(t > TEST_LENGTH*1000 + 200, 2, 1)) %>%
  group_by(subid, stimulus, instance) %>% # have to redo this to deal with repeating stimuli
  mutate(t = t - min(t)) %>%
  left_join(test_annotations) %>%
  filter(stimulus %in% test_annotations$stimulus) 
```




Read in test AOIs.

```{r}
source("loading_helpers/load_aois.R")
test_aois <- get_test_aois() %>%
  select(-Time) %>%
  rename(target = aoi_name) %>%
  group_by(target) %>%
  distinct() %>%
  mutate(top_left_x = top_left_x,
         bottom_right_x = bottom_right_x) #* 1209/1680
```

Merge and process aois. 

We need t to be more regular. Let's do something basic where we just round it to the nearest 50ms. 

```{r}
test_all_aoi_data <- left_join(test_data, test_aois) %>%
  mutate(in_aoi = (x >= top_left_x - AOI_BUFFER) & 
           (x <= bottom_right_x + AOI_BUFFER) &
           (y >= top_left_y - AOI_BUFFER) &
           (y <= bottom_right_y + AOI_BUFFER)) %>%
  group_by(stimulus, instance) %>%
  group_by(subid, stimulus, instance) %>%
  mutate(t = round(t / 50) * 50, 
         onset = round(onset / 50) * 50) %>%
  mutate(t_onset = t - onset) 
```

Let's do some checks on the quality of the ET data. 
```{r}
ggplot(test_all_aoi_data, aes(x = x)) + 
  geom_histogram() +
  facet_wrap(~stimulus)
```

```{r}
ggplot(test_all_aoi_data, aes(x = x, y = y)) + 
  geom_point() + 
  geom_rect(aes(xmin = top_left_x, 
                xmax = bottom_right_x, 
                ymin = top_left_y, 
                ymax = bottom_right_y), fill = NA, col = "black", lty = 2) + 
  facet_wrap(~stimulus) 
```


```{r}
test_means <- test_all_aoi_data %>%
  group_by(t_onset, stimulus, instance, type) %>%
  summarise(correct = mean(in_aoi, na.rm=TRUE)) 
```


```{r}
ggplot(filter(test_means, stimulus == "l_balloon_sock.jpg"), 
       aes(x = t_onset, y = correct)) + 
  geom_point()
```

```{r}
ggplot(filter(test_means, type == "Familiar"), 
       aes(x = t_onset, y = correct)) +
  geom_point() + 
  geom_hline(yintercept = .5, lty = 2) +
  geom_vline(xintercept = 0, lty = 3)
```


```{r}
# 
# test_other_data <- test_all_aoi_data %>%
#   group_by(subid, stimulus, instance, t, type) %>%
#   summarise(num_in = sum(in_aoi)) %>%
#   filter(is.na(num_in) | num_in == 0) %>%
#   ungroup() %>%
#   rename(aoi_name = num_in) %>%
#   mutate(aoi_name = as.factor(aoi_name))
# 
# test_aoi_data <- test_all_aoi_data %>%
#   filter(in_aoi) %>%
#   select(subid, stimulus, instance, type, t, aoi_name) %>%
#   bind_rows(test_other_data) %>%
#   ungroup() %>%
#   arrange(subid, stimulus, instance, t) %>%
#   left_join(test_annotations) %>%
#   filter(!is.na(target)) %>%
#   rowwise() %>%
#   mutate(aoi = if(is.na(aoi_name)) as.character(NA)
#          else if(aoi_name == target) "Target"
#          else if(aoi_name == "0") "Other"
#          else "Competitor") %>%
#   mutate(onset = floor(FRAME_RATE * onset) / FRAME_RATE) %>%
#   group_by(type, trial) %>%
#   mutate(time = trunc(time - onset)) %>%
#   rowwise() %>%
#   mutate(time = closest(time)) 

```


```{r}
ms <- test_aoi_data %>%
  group_by(t) %>%
  summarise(correct = mean(aoi == "Target", na.rm=TRUE) / 
              mean(aoi %in% c("Target","Competitor"), na.rm=TRUE))

ggplot(ms, 
       aes(x = t, y = correct)) + 
  geom_point()
  
```


# Training

```{r}
learn_data <- all+results %>%
  filter(stimulus %in% unlist(LEARN_STIM)) %>%
  group_by(subid, stimulus) %>%
  zero_times(., LEARN_STIM_LENGTH)


train_annotations <- read_csv(paste0("metadata/aois/", 
                                     VIDEOS[video], "_trains.csv"))


source('loading_helpers/load_aois.R')
train_aois <- get_train_aois(video = VIDEOS[video]) %>%
  rowwise() %>%
  mutate(Time = closest(Time)) %>%
  filter(!str_detect(aoi_name, "hand")) %>%
  rename(t = Time)

  
```


```{r}

train_all_aoi_data <- left_join(learn_data, train_aois) %>%
  filter(!is.na(aoi_name)) %>%
  mutate(in_aoi = (x_mean >= top_left_x - AOI_BUFFER) & 
           (x_mean <= bottom_right_x + AOI_BUFFER) &
           (y_mean >= top_left_y - AOI_BUFFER) &
           (y_mean <= bottom_right_y + AOI_BUFFER)) %>%
  ungroup()

```

```{r}

train_other_data <- train_all_aoi_data %>%
  summarise(num_in = sum(in_aoi)) %>%
  filter(is.na(num_in) | num_in == 0) %>%
  ungroup() %>%
  rename(aoi_name = num_in) %>%
  mutate(aoi_name = as.factor(aoi_name))

train_aoi_data <- train_all_aoi_data %>%
  filter(in_aoi) %>%
  select(subj, instance, time, aoi_name) %>% #for reflook4 dunno
  bind_rows(train_other_data)

train_annotated_data <- bind_rows(lapply(1:nrow(train_annotations), function(x) {
  filter(train_aoi_data, time >= as.numeric(train_annotations[x,"start"]) & 
           time <= as.numeric(train_annotations[x,"end"])) %>%
    cbind(train_annotations[x,])})) %>%
  rowwise() %>%
  mutate(aoi = if(is.na(aoi_name)) as.character(NA)
         else if(tolower(aoi_name) == tolower(Target)) "Target"
         else if(tolower(aoi_name) == tolower(Competitor)) "Competitor"
         else if(tolower(aoi_name) == tolower(Face)) "Face"
         #            else if(!is.na(Other_Face) & 
         #                    tolower(aoi_name) == tolower(Other_Face)) "Other Face"
         else if(tolower(aoi_name) == "0") "None"
         else "Other") %>%
  select(-aoi_name, -Target, -Competitor, -Face, -Hand) %>%
  #  -Other_Face, -Hand) %>%
  mutate(window_type = if(time >= start & 
                          time < name1) "baseline"
         else if(time >= name1 & 
                 time < look) "name_look"
         else if(time >= look &
                 time < name2) "look_name2"
         else if(time >= name2 &
                 time < initiate_reach) "name2_reach"
         else if(time >= initiate_reach &
                 time < point_of_contact) "reach_contact"
         else if(time >= point_of_contact &
                 time <= end) "contact_end"
         else "NA") %>%
  ungroup() %>%
  filter(window_type != "NA") %>%
  mutate(window_type = factor(window_type, 
                              levels = c("baseline", "name_look", "look_name2",
                                         "name2_reach", "reach_contact",
                                         "contact_end"))) %>%
  select(-start, -name1, -look, -name2, -name3,
         -initiate_reach ,-point_of_contact, -end) %>%
  group_by(subj, trial) %>%
  mutate(time = time - min(time)) %>%
  rowwise() %>%
  mutate(time = closest(time))
```


# Get all times in AOIS



<!-- ## Add Demographic Data  -->

<!-- demo_data <- fread(paste0('raw_data/demo_data/',VIDEOS[video], -->
<!--                              "/", GROUP,'.subinfoR4.csv')) -->

<!-- if(VIDEOS[video] == "soc_word"){ -->
<!--   demo_data %<>% -->
<!--     select(subid, age, gender, english, parent_education, premature) %>% -->
<!--     rename(subj = subid) -->

<!--   test_aoi_data %<>% left_join(demo_data) -->
<!--   train_annotated_data %<>% left_join(demo_data)  -->
<!-- } else if(GROUP == "child") { -->

<!--   #  -->
<!--   # tmp <- raw_child_test_data %>% -->
<!--   #   rowwise() %>% -->
<!--   #   mutate(english = if(is.na(english)) as.numeric(NA) -->
<!--   #          else if(english == 6) 100 -->
<!--   #          else if(english == 5) 90 -->
<!--   #          else if(english == 4) 75 -->
<!--   #          else if(english == 3) 50 -->
<!--   #          else if(english == 2) 25 -->
<!--   #          else if(english == 1) 5 -->
<!--   #          else 0) -->
<!--   #  -->
<!--   # tmp <- tmp %>% -->
<!--   #   rowwise() %>% -->
<!--   #   mutate(premie = if(is.na(premie)) as.logical(NA) -->
<!--   #          else if(premie == 1) FALSE -->
<!--   #          else TRUE) -->

<!--   demo_data %<>% -->
<!--     select(subid, dot, dob, gender, english, premie) %>% -->
<!--     mutate_each(funs(mdy), dot, dob) %>% -->
<!--     mutate(age = (dot - dob)/dyears(1), -->
<!--            gender = factor(gender, labels = c("Male", "Female",NA))) %>% -->
<!--     rename(subj = subid) %>% -->
<!--     select(-dot, -dob) -->
<!--   test_aoi_data %<>% left_join(demo_data) -->
<!--   train_annotated_data %<>% left_join(demo_data)  -->
<!-- } else if(GROUP == "ASD") { -->
<!--   demo_data %<>% -->
<!--     select(subid, dot, dob, gender) %>% -->
<!--     mutate_each(funs(mdy), dot, dob) %>% -->
<!--     mutate(age = (dot - dob) / dyears(1), -->
<!--            gender = factor(gender, levels = c("m", "f"), -->
<!--                            labels = c("Male", "Female"))) %>% -->
<!--     rename(subj = subid) %>% -->
<!--     select(-dot, -dob) -->
<!--   test_aoi_data %<>% left_join(demo_data) -->
<!--   train_annotated_data %<>% left_join(demo_data)  -->
<!-- } else if(GROUP == "long") { -->
<!--   demo_data %<>% -->
<!--     select(subid, dot, dob, gender) %>% -->
<!--     mutate_each(funs(mdy), dot, dob) %>% -->
<!--     mutate(age = (dot - dob)/dyears(1), -->
<!--            gender = factor(gender, labels = c("Male", "Female"))) %>% -->
<!--     rename(subj = subid) %>% -->
<!--     select(-dot,-dob) -->
<!--   test_aoi_data %<>% left_join(demo_data) -->
<!--   train_annotated_data %<>% left_join(demo_data)  -->
<!-- } -->
<!-- ############################################################################### -->
<!-- ############################## Write Output Data ############################## -->
<!-- ############################################################################### -->
<!-- write_csv(test_aoi_data, paste0('processed_data/csvs/',VIDEOS[video], "/", -->
<!--                                GROUP,'/test_data.csv')) -->
<!-- write_csv(train_annotated_data, paste0('processed_data/csvs/', -->
<!--                                       VIDEOS[video], "/",  -->
<!--                                       GROUP,'/train_data.csv')) -->

<!-- tmp <- train_annotated_data %>% -->

<!--   group_by(time, trial, subj) %>% -->
<!--   summarise(correct = sum(aoi == "Target",na.rm=T)/ -->
<!--               (sum(aoi=="Target",na.rm=T)+sum(aoi=="Competitor",na.rm=T))) %>% -->
<!--   summarise(correct = mean(correct, na.rm = T)) %>% -->
<!--   summarise(correct = mean(correct, na.rm = T)) -->




<!-- # Get Trial Data -->

<!-- ```{r} -->
<!-- zero_times <- function(gaze_data, stim_length, split = FALSE) { -->

<!--   gaze_data <- gaze_data %>% -->
<!--     mutate(t = (t - min(t))/1000000) %>% -->
<!--     mutate(instance = ifelse(split & (t > TEST_LENGTH + .2), -->
<!--                              2, 1)) %>% #reflook4 issue -->
<!--      group_by(instance, add = TRUE) %>% -->
<!--      mutate(t = (t - min(t))) -->

<!--   if(!is.na(stim_length)) -->
<!--     gaze_data %<>% mutate(t = (t - (max(t) - stim_length))) -->

<!--   gaze_data %>% -->
<!--     filter(t > 0) %>% -->
<!--     mutate(t = trunc(floor(FRAME_RATE * t) / FRAME_RATE))%>% -->
<!--     group_by(t, add=TRUE) %>% -->
<!--     summarise_each(funs(mean = mean(., na.rm = T)), c(x, y)) -->
<!-- } -->

<!-- ``` -->
